\setmainfont{Quicksand}[
	UprightFont = *-Medium,
	BoldFont = *-Bold]
\raggedright

\section{The Grid}
%During the game, the players will place tiles in the play area. These tiles will be organized into a \textbf{grid} made up of \textbf{rows} and \textbf{columns}. A row is a group of tiles that are on the same horizontal line.  A column is a group of tiles that are on the same vertical line. The grid should have no more than six rows and six columns.
%
%A \textbf{line} is a generic term that can refer to either a single row or a single column of the grid. Each line can contain no more than one tile with each glyph and one tile with each color.

During the game, the players will place tiles in the play area. These tiles will be organized into a \textbf{grid} made up of vertical and horizontal \textbf{lines}.

Each line can contain no more than one tile with each glyph and one tile with each color.

The grid can have no more than six vertical lines and six horizontal lines.

\subsection{Notes}
At the beginning of the game, the grid is empty.

Lines do not need to be contiguous.
If two tiles are on the same line then they must have different glyphs and colors.

\section{Set Up}
The tiles should be placed face up to one side of the play area. These tiles comprise the \textbf{supply}. The supply should be arranged in a square. Each column should have all tiles of a given glyph and each row should have all tiles of a given color.

The players should randomly determine which one of them will be the \textbf{first player}.

\section{The Draft}
Starting with the first player, the players then take turns \textbf{drafting} tiles. To draft a tile, a player should choose one tile from the supply and add that tile to their \textbf{hand}.

The draft is complete when both players have four tiles in their hand.

\subsection{Notes}
All tiles should be visible to both players at all times.  This includes the supply, the grid, and both players' hands.

